\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[official]{eurosym}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning}

% Standardized TikZ configuration
\tikzset{
    myblock/.style={
        rectangle, 
        draw, 
        fill=blue!10, 
        text width=12cm, 
        align=center, 
        rounded corners, 
        minimum height=1.2cm,
        thick
    },
    myline/.style={
        draw, 
        thick, 
        ->, 
        >=Stealth
    }
}

\def\myperiod{.}

\def\halwebref#1{\href{https://hal.inria.fr/hal-#1}%
     {{https://hal.inria.fr/hal-#1}}}

\def\webref#1{\href{#1}%
     {{#1}}}

\newcommand{\copubsitemref}[4]{
  \item#1: 
  {\def\bfdefault{bx}\bf\emph{#2\myperiod}} #3.
  \\{\small\tt\webref{#4}}
}

\newcommand{\copubsitemhalref}[4]{
  \item#1: 
  {\def\bfdefault{bx}\bf\emph{#2\myperiod}} #3.
  \\{\small\tt\halwebref{#4}}
}
\newcommand{\copubsitemfullref}[5]{
  \item#1: 
  {\def\bfdefault{bx}\bf\emph{#2\myperiod}} #3.
  \\{\small\tt\webref{#4}}
  \\{\small\tt\halwebref{#5}}
}

\newcommand{\TODO}[1]{{\color{red}TODO: #1}}

\usepackage{marginnote}
\newcommand{\matteo}[1]{{\color{magenta}#1}}
\newcommand{\mmatteo}[1]{\marginpar{\small{\color{magenta}M: #1}}}

\newcommand{\memb}[4]{\item #1, \emph{#2}, {\tt #3}\\ #4}
\newcommand{\fmemb}[4]{\item #1, \emph{#2}, {\tt #3}}
\newcommand{\sacaddr}{1 rue Honor\'{e} d'Estienne d'Orves,
%B‰timent Alan Turin,
%Campus de l'\'{e}cole Polytechnique,
Inria \& \'{E}cole Polytechnique,
91120 Palaiseau,
France}
\newcommand{\sacaddrb}{Inria Saclay, 1 rue Honor\'{e} d'Estienne d'Orves,
B\^{a}timent Alan Turin,
Campus de l'\'{E}cole Polytechnique,
%Inria \& \'{e}cole Polytechnique,
91120 Palaiseau,
France}

\begin{document}

\begin{center}
  \bf Application to the Sophie Germain funding scheme 
  \\[1ex]
  \normalsize\rm
  Research Track: Artificial intelligence
    \\[2ex]
  \large\bf  ARGUS: AI-Guided Automated Reasoning for Non-Classical Logics
%5  \\[1ex]
%  \normalsize\rm
 % Priority Theme: Artificial intelligence, including ethics
\end{center}

\paragraph*{Abstract.}

Automated theorem proving (ATP) is a cornerstone of modern software verification, industrial optimization, and system security. However, when moving beyond classical constraints to handle qualified truth, constructive reasoning, or inconsistent data, traditional symbolic solvers suffer from severe performance degradation caused by vast heuristic search spaces. The ARGUS project addresses this challenge by pioneering a hybrid neuro-symbolic paradigm that embeds machine learning directly into state-of-the-art non-classical reasoning engines. Bringing together premier logic, proof theory, and verification teams from Inria Saclay and University College London, this bilateral initiative deploys data-driven models to optimize sequent calculus derivations and prune Satisfiability Modulo Theories (SMT) encodings for Restricted Non-Deterministic Matrices (RNmatrices). The project safely boosts proving speeds and countermodel clarity without compromising formal logical correctness, by completely decoupling the statistical learning layer from an absolute symbolic verification kernel. Ultimately, ARGUS delivers an open-source, user-oriented platform that bridges the gap between statistical AI and formal logic, creating the critical mass required to scale these breakthroughs into a larger Horizon Europe research program.

\subsection*{1. Presentation of the teams}

\subsubsection*{French Team.}

The French Team consists of members of the {\sc Partout} project which is joint between Inria Saclay and LIX (UMR 7161) at \'{E}cole Polytechnique. This team brings extensive expertise in all areas of logic, formal verification, and proof theory, which is crucial for the success of the project.

\begin{itemize}
\fmemb{PI: Kaustuv Chaudhuri}{Charg\'{e} de recherche}{kaustuv@chaudhuri.info}{\sacaddr}

\fmemb{Dale Miller}{Directeur de recherche}{dale.miller@inria.fr}{\sacaddr}

\fmemb{Lutz Stra\ss burger}{Directeur de recherche}{lutz@lix.polytechnique.fr}{\sacaddr} 

\fmemb{Beniamino Accattoli}{Charg\'{e} de recherche}{beniamino.accattoli@inria.fr}{\sacaddr}

\fmemb{Victoria Barrett}{Postdoc}{victoria.barrett@inria.fr}{\sacaddr}

\fmemb{Arunava Gantait}{PhD student}{Arunava.Gantait@lix.polytechnique.fr}{\sacaddr}

\end{itemize}
The postal address for all team members is:\\[.5ex] \sacaddrb.


\subsubsection*{British Team.}

The British team is located at University College London, and it comprises experts in logic and verification, as well as machine learning and proof theory. 
\begin{itemize}

\fmemb{PI: Elaine Pimentel}{Professor of logic and Computation}{e.pimentel@ucl.ac.uk}{66-72 Gower St., University College London,
WC1E 6EA London, UK}

\fmemb{David Pym}{Professor of Information, Logic, and Security}{d.pym@ucl.ac.uk}{66-72 Gower St., University College London,
WC1E 6EA London, UK}

\fmemb{Victor Barroso Nascimento}{Postdoc}{victorluisbn@gmail.com}{66-72 Gower St., University College London,
WC1E 6EA London, UK}

\fmemb{Katya Piotrovskaya}{PhD student}{kate.piotrovskaya.21@ucl.ac.uk}{66-72 Gower St., University College London,
WC1E 6EA London, UK}

\fmemb{Maria Os\'{o}rio}{PhD student}{ucacmo0@ac.ucl.uk}{66-72 Gower St., University College London,
WC1E 6EA London, UK}

\fmemb{Joaquim Torres Waddington}{PhD student}{joaquim.waddington.24@ucl.ac.uk}{66-72 Gower St., University College London,
WC1E 6EA London, UK}

\fmemb{Arghya Chackrabarty}{PhD student}{arghya.chakrabarty.20@ucl.ac.uk}{66-72 Gower St., University College London,
WC1E 6EA London, UK}

\end{itemize}
%
The postal address for all members of the British team is:\\[.75ex]
66-72 Gower St., University College London,
WC1E 6EA London, UK



%\TODO{make smooth; maybe move after the project}

\subsection*{2. The Research Project}

\paragraph{State of the Art.}
Over the past few years, we have developed several automated reasoning methods for non-classical logics. These methods follow two complementary approaches. The first is proof-theoretic and is based on deductive rules, particularly sequent calculi. The second is semantic and relies on finite-valued non-deterministic matrices, or RNmatrices, and restricted classes of valuations.

Our proof-theoretic methods have been implemented in rewriting logic, using rewriting and narrowing as the underlying computational mechanisms. In this setting, the inference rules of a sequent calculus are represented as rewrite rules, and the search for a derivation is reduced to a reachability problem. The same reflective infrastructure can also be used to reason about the proof system itself, for instance, to establish admissibility, invertibility, identity expansion, and cut elimination.

Our semantic methods generate finite truth tables or encode the corresponding valuation constraints into satisfiability-modulo-theories, or SMT, problems. In recent work, we developed modular Nmatrix-based decision procedures for modal logics, with a companion prover, TRiNity. These procedures search for partial valuations that satisfy the semantic dependencies imposed by the logic. When a formula is not valid, the resulting valuations can be used to construct a countermodel and, in the modal setting, to recover an associated Kripke-style structure.

Although these approaches provide formally justified decision and semi-decision procedures, their efficiency remains highly dependent on a number of heuristic choices.

For sequent systems, proof search depends on decisions such as which inference rule to apply, which occurrence of a formula should be selected as principal, which pending goal should be explored first, and which previously established lemmas should be made available. Poor choices may produce unnecessarily large search trees, repeated subproblems, or non-terminating branches.

For RNmatrix-based methods, the procedure must explore potentially large spaces of partial valuations. Its performance depends on the order in which subformulas are considered, the truth values assigned to them, and the selection of supporting valuations required by the semantic dependencies. When the problem is translated into SMT, similar decisions determine the branching behavior of the solver.

A further difficulty concerns the implementation of the SMT encodings. Semantically equivalent representations may behave very differently depending on the solver and the class of formulas under consideration. Truth values may, for example, be represented using algebraic datatypes, bit vectors, integers, or collections of Boolean variables. Functions and semantic relations may be encoded using uninterpreted functions, arrays, finite maps, or explicit Boolean constraints. Choosing an appropriate representation and solver configuration currently requires significant expert knowledge and manual experimentation.

Finally, the existing implementations are primarily research prototypes. Making them accessible to a wider community requires additional work on parsers, user interfaces, interoperability, visualization, and explanation facilities. In particular, users should be able to inspect a generated sequent derivation, understand why a proof attempt failed, examine a falsifying valuation, and visualize the corresponding countermodel.

\paragraph{Research programme.}
The central hypothesis of this project is that artificial intelligence can substantially improve the efficiency and usability of these automated reasoning procedures without compromising their logical guarantees.

The project will follow a neuro-symbolic architecture in which AI components are used only to guide or configure the search. All results proposed by an AI component will be checked by the existing symbolic infrastructure. A positive answer will therefore be accompanied by a formally checkable derivation or proof certificate, while a negative answer will be justified by an explicit valuation or countermodel.
%
This separation between a heuristic AI layer and a trusted symbolic kernel is {\em essential}. It allows the project to benefit from statistical learning while preserving the soundness of the underlying deductive and semantic methods.

%Scientific objectives
We intend to achieve this by the following four steps:
\begin{enumerate}
\item {\em Learning strategies for sequent proof search.}
The first objective is to develop learned strategies for proof search in sequent calculi implemented in rewriting logic.
%
The current procedures may generate several applicable rewrites at a given proof state. The project will investigate models that rank these alternatives according to their estimated probability of contributing to a successful and economical proof. The learned strategy may guide several related decisions: (i) selection of the next inference rule; (ii)selection of the principal formula or formula occurrence; (iii) ordering of the premises generated by a rule; (iv) selection of the next pending proof obligation; (v) prediction of useful admissibility or invertibility lemmas; (vi) detection of branches that are unlikely to succeed within the available resources.

Training data will initially be extracted from successful and unsuccessful execution traces produced by the existing tools. A proof state can be represented using syntactic features, formula trees, multisets of formulas, or graph representations that make dependencies between subformulas explicit. Supervised learning can then be used to imitate successful proof traces. This approach may subsequently be complemented by reinforcement learning or online learning, where the reward reflects proof success, proof length, execution time, or the number of explored states.

The learned strategy will not remove any inference rule from the calculus. It will rank alternatives and allocate computational resources among them. When the learned component is uncertain or unsuccessful, the tool will be able to fall back on an exhaustive or fairness-preserving search strategy. The resulting procedure will therefore retain the guarantees of the original symbolic system whenever the underlying exhaustive procedure terminates.

\item  {\em AI-guided construction of falsifying RNmatrix valuations.}
The second objective is to accelerate validity checking by guiding the search for falsifying partial valuations and countermodels.
%
Given a formula, the RNmatrix procedure must assign truth values to its subformulas while satisfying the non-deterministic truth tables and the additional restrictions imposed by the logic. When a truth value introduces a semantic dependency, the procedure may also need to identify another valuation that supports it. This produces several opportunities for learning-based guidance.

A model may predict promising truth values for atomic formulas and selected subformulas, prioritizing assignments that are likely to make the target formula non-designated. It may also rank candidate supporting valuations or predict which semantic dependencies are likely to cause a partial valuation to be rejected. Information extracted from unsuccessful attempts can be used to learn recurring conflict patterns, analogously to the way symbolic solvers record combinations of decisions that cannot lead to a solution.

The AI component may be used either in the explicit truth-table procedure or as a source of branching hints for an SMT encoding. In both cases, the predictions will remain heuristic: a proposed valuation must satisfy the complete RNmatrix constraints before it can be reported as a counterexample.

An additional goal will be the construction of small and intelligible countermodels. The learned component may guide the search toward valuations involving fewer rows, fewer supporting relations, or simpler assignments. This could improve both performance and the explanatory quality of the generated results.

\item {\em Automatic selection and synthesis of SMT encodings.}
The third objective is to automate the engineering of solver-specific encodings.
%
The project will define a family of semantically equivalent encoding patterns for RNmatrices and related logical structures. These patterns may differ in their representation of truth values, valuations, non-deterministic operators, finite relations, and semantic dependencies.

Machine-learning-based algorithm selection will then be used to choose among: (i) different SMT solvers; (ii) different representations, such as bit vectors, algebraic datatypes, integers, arrays, or Boolean vectors; (iii) alternative axiomatisations of the same semantic constraints; (iv) solver parameters and preprocessing options; (v) eager or incremental generation of semantic constraints.

The selection will be based on features of the input formula and logic, including its size, modal depth, connective distribution, number of repeated subformulas, expected truth-value domain, and structure of the required semantic dependencies.

Large language models may additionally assist in producing initial implementations of new encodings or translations between solver languages. However, generated encodings will not be trusted directly. They will be validated through differential testing, comparison with existing decision procedures, property-based testing, and, where possible, formal proofs of equivalence.

The scientific goal is not merely to automate programming tasks, but to develop a systematic and reusable methodology for learning which symbolic representation is best suited to a given reasoning problem.

\item {\em Trustworthy explanations and user-oriented tools.}
The fourth objective is to turn the existing prototypes into an accessible reasoning environment.
%
The platform will provide a common interface through which users can select a logic, enter a formula or sequent, choose an analysis, and inspect the result. AI-assisted language processing may be used to translate between different concrete syntaxes or to help users formulate a query. Nevertheless, the internal formal representation will always be displayed and validated before the analysis is performed.

For valid formulas and derivable sequents, the platform will reconstruct and visualize the corresponding proof tree. It will identify the inference rule used at each step and make explicit any auxiliary lemma or structural property on which the derivation depends.

For invalid formulas, it will display the falsifying RNmatrix valuation, explain the semantic dependencies between its rows, and, when applicable, construct a graphical Kripke-style countermodel. Natural-language explanations will be generated from these checked symbolic objects rather than directly from the output of a language model. This will ensure that explanations remain grounded in the formal evidence produced by the tool.

The platform will expose both a graphical web interface and a programmatic API, making it possible to use the developed procedures in teaching, experimentation, and other verification tools.
\end{enumerate}

\paragraph{Work packages.}
\begin{itemize}
\item[\bf WP~1] The project will begin with the construction of a common benchmark and trace infrastructure. The existing sequent and RNmatrix implementations will be instrumented to record proof states, candidate decisions, successful and unsuccessful branches, solver calls, generated valuations, and execution costs.

The benchmark will combine examples from the literature with automatically generated formulas. It will cover different families of propositional, modal, intuitionistic, paraconsistent, and substructural logics supported by the existing methods. Care will be taken to separate training and evaluation data not only by individual formulas, but also by formula families and logical systems. This will make it possible to evaluate whether the learned strategies generalize beyond minor variations of previously observed examples.

\item[\bf WP~2]  The AI-guided procedures will be compared with the existing exhaustive search strategies and manually designed heuristics. The main evaluation criteria will include: (i) the number and percentage of instances solved within fixed time and memory limits; (ii) total execution time and memory consumption; (iii) the number of explored proof states or partial valuations; (iv) proof length and countermodel size; (v) the overhead introduced by the learned components; (vi) generalization to previously unseen formula structures and logical systems; (vii) the percentage of generated results successfully validated by the symbolic checker.

\item[\bf WP~3]  Ablation experiments will determine the contribution of individual features and learning mechanisms. For example, rule selection, formula selection, lemma prediction, and subgoal ordering will be evaluated both independently and in combination.
\end{itemize}
\paragraph{Expected outcomes.}
The project is expected to produce a new generation of hybrid automated reasoning tools in which AI-based guidance is combined with formally verified symbolic procedures.

Its main outcomes will be:
\begin{itemize}
\item learned proof-search strategies for sequent systems specified in rewriting logic;

\item AI-guided algorithms for constructing RNmatrix valuations and minimal countermodels;

\item methods for automatically selecting SMT solvers, encodings, and configurations;

\item a benchmark suite containing formulas, proof traces, valuations, and solver-performance data;

\item a unified open-source platform providing proof search, validity checking, countermodel generation, visualization, and formally grounded explanations.
\end{itemize}
Beyond the immediate performance improvements, the project will investigate a broader scientific question: {\em how can statistical methods be incorporated into automated deduction without weakening the formal guarantees that distinguish theorem provers from general-purpose generative systems?}

The expected result is an architecture in which AI is used where heuristics and prediction are most valuable, while rewriting logic, RNmatrix semantics, and SMT solving provide the trusted foundations needed to certify every final answer.

\paragraph*{Historic Context of the Collaboration.}
The collaboration builds on several years of joint work between Inria Saclay and UCL on proof theory, automated deduction, and RNmatrix semantics. The teams have co-authored multiple publications, jointly supervised students, and developed complementary reasoning tools that provide the technical foundation for ARGUS.

\paragraph{Plans for continued collaboration and funding prospects after the project.}

%, notably a potential Horizon Europe application}

The project is intended to create a critical mass necessary to launch a larger program under Horizon Europe. We plan to organise workshops and invite external experts to eventually enlarge the consortium. A successful outcome of this project will allow us to attract further funding for the research programme outlined above.
This initiative aims at building a strong foundation and demonstrating the potential impact,  and to secure further funding and support for extensive research and development efforts within the Horizon Europe framework.


\paragraph{Long term outcomes of the project.} %%, including potential societal and industrial outcomes}
The successful execution of this project is expected to yield substantial, long-term impacts across both the automated reasoning and formal verification communities:

\begin{itemize}
    \item \textbf{A Standardized API for AI-Guided Semantic Provers.} The project will result in an open-source, modular extension to the TRiNity engine. By standardizing the interface through which neural models pass valuation and row heuristics to SMT back-ends, we establish an extensible infrastructure that allows other researchers to swap in different neural architectures (e.g., Graph Transformers vs. Reinforcement Learning agents).
    \item \textbf{Universal Benchmark Libraries for Non-Classical Logics.} To train the models, the project will generate a massive dataset of non-classical formulas across the $C_n$ hierarchy, intuitionistic logic, and modal systems, mapping formulas to their corresponding RNmatrix search paths and minimal countermodels. This will serve as a permanent benchmark library for future AI-driven ATP systems.
    \item \textbf{Accelerated Formal Verification for Specialized Systems.} Non-classical logics are critical for verifying distributed networks (modal logic), cryptographic protocols (intuitionistic logic), and database systems handling contradictory data (paraconsistent logic). Providing an order-of-magnitude speedup in these domains will make practical formal verification viable for complex, safety-critical industrial applications that classical SAT/SMT tools cannot naturally handle.
\end{itemize}

\paragraph*{Risk Analysis \& Mitigation Strategies.}
Given the interdisciplinary nature of fusing deep learning models with formal symbolic reasoning, several technical and structural risks have been identified alongside concrete mitigation pathways.

%\begin{table}[htbp]
%\centering
%\caption{Risk Assessment and Mitigation Matrix}
%\label{tab:risks}
%\begin{tabular}{p{3.5cm}llp{6.5cm}}
%\toprule
%\textbf{Identified Risk} & \textbf{Probability} & \textbf{Impact} & \textbf{Mitigation Strategy} \\ \midrule
%\textbf{Data Sparsity for Training} & Medium & High & Use synthetic data generation engines by mutating existing templates and utilizing structural bootstrapping techniques. \\ \addlinespace
%\textbf{Neural Inference Latency Bottleneck} & High & Medium & Implement lightweight, distilled models (e.g., highly compressed GNNs) and restrict neural inference to complex subformulas above a specified nesting threshold. \\ \addlinespace
%\textbf{Poor Heuristic Convergence} & Medium & Low & \textbf{Architectural Safeguard:} The SMT layer guarantees absolute correctness. If neural guidance degrades, the engine falls back gracefully to standard TRiNity search heuristics. \\ \bottomrule
%\end{tabular}
%\end{table}
\begin{enumerate}
    \item \textbf{The Data Sparsity Challenge.} Unlike classical logic, standard libraries for non-classical systems (like the ILTP library) are relatively small. Training deep neural networks requires massive quantities of labeled data. 
    \\ \textit{Mitigation:} We will implement a synthetic formula generator that systematically construct valid and invalid formulas by mutating known matrix properties, thereby creating a balanced and rich training space.
    \item \textbf{Inference Overhead vs. Prover Speed.} Complex graph or transformer model passes could introduce a runtime overhead that cancels out the speedups gained by pruning the SMT search space.
    \\ \textit{Mitigation:} Models will be aggressively quantized and distilled into lightweight edge architectures. Furthermore, neural prediction will only trigger at specified structural decision points (e.g., when encountering heavily quantified row constraints or multi-level modal jumps).
    \item \textbf{Heuristic Misdirection (Hallucination).} The neural model might predict faulty row selections or misleading valuation biases, guiding the prover into highly inefficient search paths.
    \\ \textit{Mitigation:} Because soundness and completeness are fully decoupled from the neural layer, bad predictions never compromise proof integrity. If a search path exceeds a localized timeout, the prover automatically dampens the neural weights and defaults to standard SMT backtracking.
\end{enumerate}

\pagebreak

\section*{Annexes}

\subsection*{Calendar for the project}

\begin{itemize}
    \item Start date: 1 January 2027
    \item Duration 16 months
    \item Main milestones: We expect each of the four work packages to take about 3-4 months, giving us room to adjust in case of unforeseen difficulties. The last two month are reserved for writing up our result in form of publications in prestigious conferences and journals.
    \begin{itemize}
        \item  April 2027: Learning strategies for proof search (sequents/matrices)
        \item July 2027: Automatic selection and synthesis of SMT encodings
        \item November 2027: Trustworthy explanations and user-oriented tools
        \item January 2028: Benchmark the results
    \end{itemize}
\end{itemize}


\subsection*{Financial details}

\subsubsection*{a. Planned budget}

\par
%Observe that: ``The funds available in this call are provided by the French government and will be allocated to French researchers. Although this funding is limited to French researchers, only applications jointly submitted by French and British PIs to the French Steering Committee are declared eligible. British researchers will have to apply to the British call, which will be launched separately from the French one.''

%Hence the budget should be only for the French side.

\smallskip

%FRANCE

\begin{tabular}{|l|r|l|}
\hline
Type of expense & Amount (in \euro) & Description \\
\hline
Travel & 22 800  & mutual visits and conference attendance\\
Equipment & 3 000 & 2 laptops \\
Essential consumable materials & 200 & \\
Documentation &  - & \\
Publication & 2 000 & \\
%Field work (if relevant) & & \\
Research grants & - & \\ %%two one-month research visits abroad\\
Other & 11 000 & workshop organisation\\
\hline
\bf Total & \bf 39 000 & \\
\hline
\end{tabular}


\bigskip

\subsubsection*{b. Justification of expenses}

\subsection{Justification of Expenses}
The proposed budget is directly tied to the core objectives of the project, focusing on maximizing the collaborative expertise of the two teams, enabling intensive neural network training, and fostering wider research consortiums. 

\begin{itemize}
    \item \textbf{Travel and Subsistence (\euro 22,800):} Since this is a joint initiative between PARTOUT (France) and PPLV (UK), face-to-face collaboration is paramount. The bulk of the budget is allocated to cross-border research exchanges, specifically prioritizing PhD students and junior researchers. 
    \begin{itemize}
        \item \textit{Mutual Bilateral Visits (\euro 17,800):} Covers 10 distinct one-week research visits (5 from France to the UK, and 5 from the UK to France). Each visit is budgeted at \euro 700, encompassing \euro 200 for return train travel and \euro 500 for local accommodation and subsistence (\euro 100/day for 5 days). It also covers 4 one-month visits from PhD students and postdocs, each visit is budgeted at \euro 2,700: \euro 200 for return train travel and \euro 2,500 for local accommodation and subsistence.
        \item \textit{Conference Attendance (\euro 5,000):} Allocates \euro 2,500 each for two PhD students to present research results at major international peer-reviewed conferences. This includes registration fees (\euro 800), transportation (\euro 700), and accommodation/subsistence (\euro 1,000).
    \end{itemize}

    \item \textbf{Equipment (\euro 3,000):} To support the computational overhead of training Graph Neural Networks (GNNs) and benchmarking Large Language Models (LLMs) locally, the project requires 2 high-performance laptops equipped with dedicated GPU acceleration capabilities, budgeted at approximately \euro 1,500 each.

    \item \textbf{Consumables and Materials (\euro 200):} Covers essential day-to-day coordination materials for workspace collaboration (whiteboards, markers, and paper) as well as dedicated hardware (microphones and high-definition cameras) to ensure seamless, high-quality video-conferencing during hybrid team meetings.

    \item \textbf{Publication Costs (\euro 2,000):} While the teams strongly advocate for green open-access and host all primary preprints freely on HAL, this fund is strictly reserved to cover mandatory Open Access or processing fees levied by prestigious international conferences in automated reasoning.

    \item \textbf{Workshop Organisation (\euro 11,000):} To establish the critical mass required for future Horizon Europe bids, the project will host two milestone workshops--one in France and one in the United Kingdom. 
    \begin{itemize}
        \item \textit{External Expert Travel (\euro 8,400):} Covers the travel and lodging for two invited international experts per workshop (\euro 1,500 airfare + \euro 600 for a 3-night hotel stay per expert).
        \item \textit{Catering and Refreshments (\euro 2,600):} Provides lunch (\euro 450/day) and two coffee breaks (\euro 90/break) across the 2-day duration of each workshop for an estimated 30 participants. Institutional lecture halls are provided free of charge by the host universities.
    \end{itemize}
\end{itemize}

\subsection*{Publications of PIs}

\subsubsection*{a. Kaustuv Chaudhuri (PI of the French team)}

\begin{enumerate}

\copubsitemfullref{Kaustuv}{Title}{Venue}{doi}{HAL\#}
\end{enumerate}

\subsubsection*{a. Elaine Pimentel (PI of the British team)}

\begin{enumerate}

\copubsitemref{R. R. Leme, C. Olarte, E. Pimentel}{Efficient Decision Procedures for RNmatrix Semantics}{LSFA 2026}{https://arxiv.org/abs/2605.01845}

\copubsitemref{R. R. Leme, C. Olarte, E. Pimentel, M. E. Coniglio}{The Modal Cube Revisited: Semantics without Worlds}{TABLEAUX 2025}{https://doi.org/10.1007/978-3-032-06085-3\textunderscore10}

\copubsitemref{C. Olarte, E. Pimentel, C. Rocha}{A Rewriting Logic Approach to Specification, Proof-search, and Meta-proofs in Sequent Systems}{Journal of Logical and Algebraic Methods in Programming vol 130, 2023}{https://doi.org/10.1016/j.jlamp.2022.100827}

\copubsitemref{S. Marin, D. Miller, E. Pimentel, M. Volpe}{From axioms to synthetic inference rules via focusing}{Annals of Pure and Applied Logic Volume 173, Issue 5, 2022}{https://doi.org/10.1016/j.apal.2022.103091}

\copubsitemref{K. Chaudhuri, J. Despeyroux, C. Olarte, E. Pimentel}{Hybrid Linear Logic, revisited}{MSCS Volume 29 Issue 8, pp. 1151-1176, 2019}{https://doi.org/10.1017/S0960129518000439}
\end{enumerate}
\end{document}